---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ensMAPDP

<!-- badges: start -->
<!-- badges: end -->

The goal of ensMAPDP is to ...

## Installation

You can install this package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mkrzak/ensMAPDP")
```

If you didn't succeed with install_github download zip of this repo, 
unzip it at any location of your computer and run: 

``` r
devtools::install_github("/yourlocation/ensMAPDP-master")
```

## Example

This is basic example to run package. Load data:

```{r example}
library(ensMAPDP)
data("X")
data("m0")
data("B0")
D = dim(X)[2]
N = dim(X)[1]
N0 = 0.5
a0 = 10
c0 = 10/N
```


```{r }
# Uncomment these lines 
#out1 <- ensMAPDP::clusterIndividual(as.matrix(t(X)), N0, m0, a0, c0, B0)
#out1
#out2 <- ensMAPDP::clusterIndividual(as.matrix(t(X)), N0, m0, a0, c0, B0)
#out2
```

## System specifications

I installed this package using Ubuntu 18.04.4 LTS, with Python 3.7.7.
Tested on MAC with specs: macOS 10.14.6, Python 3.8.3 and Python 3.7.7
